Efficient Management of Reified Statements in RDF

### 2012-06-04 paper-iswc-reification/intro.tex
added labels for the main sections and used these to cross-reference in the outline paragraph of the intro

\textbf{Outline.} We will start in Section 2 with the related work section where we provide a broader overview of works on RDF metadata beyond named graphs and RDF reification. The main idea behind {\ReifiPlus} and its main advantages over {\Reifi} are discussed in Section 3. Then, we discuss how to extend RDF and SPARQL to incorporate this reification mechanism in Section 4 and 5, respectively. We present experimental results in Section 6 and conclude in Section 7.

>>>>

\textbf{Outline.} We will start in Section~\ref{Section:RelWork} with the related work section where we provide a broader overview of works on RDF metadata beyond named graphs and RDF reification. The main idea behind {\ReifiPlus} and its main advantages over {\Reifi} are discussed in Section~\ref{Section:Discussion}. Then, we discuss how to extend RDF and SPARQL to incorporate this reification mechanism in Section~\ref{Section:DataModel} and~\ref{Section:Querying}, respectively. We present experimental results in Section~\ref{Section:Experiments} and conclude in Section~\ref{Section:Conclusion}.
